CKY Parsing With Independence Constraints

### 2015-07-03 paper.tex
Add references to related work

>>>>

There is some previous research using clause boundaries to constrain dependency
parsers \cite{Ohno2006,Husain2011,Kim2004}. This is more linguistically
motivated than our constraints; indeed, the approaches appear to rely on
processing specific to each language. It is difficult to compare with these
results directly; however, although only \cite{Ohno2006} reported parse times,
all three papers reported improved accuracy.
